### 2016-07-29 R/ITHIM.Rmd
Introduced TODO.org and NHTS data

<!--

>>>>

### NHTS

```{r NHTS}
foo <- read.csv(file = "~/GHI/data/NHTS/Ascii/DAYV2PUB.CSV", na.strings = "-9")
names(foo) <- c("HOUSEID","PERSONID","FRSTHM","OUTOFTWN","ONTD_P1","ONTD_P2","ONTD_P3","ONTD_P4","ONTD_P5","ONTD_P6","ONTD_P7","ONTD_P8","ONTD_P9","ONTD_P10","ONTD_P11","ONTD_P12","ONTD_P13","ONTD_P14","ONTD_P15","TDCASEID","HH_HISP","HH_RACE","DRIVER","R_SEX","WORKER","DRVRCNT","HHFAMINC","HHSIZE","HHVEHCNT","NUMADLT","FLAG100","LIF_CYC","TRIPPURP","AWAYHOME","CDIVMSAR","CENSUS_D","CENSUS_R","DROP_PRK","DRVR_FLG","EDUC","ENDTIME","HH_ONTD","HHMEMDRV","HHRESP","HHSTATE","HHSTFIPS","INTSTATE","MSACAT","MSASIZE","NONHHCNT","NUMONTRP","PAYTOLL","PRMACT","PROXY","PSGR_FLG","R_AGE","RAIL","STRTTIME","TRACC1","TRACC2","TRACC3","TRACC4","TRACC5","TRACCTM","TRAVDAY","TREGR1","TREGR2","TREGR3","TREGR4","TREGR5","TREGRTM","TRPACCMP","TRPHHACC","TRPHHVEH","TRPTRANS","TRVL_MIN","TRVLCMIN","TRWAITTM","URBAN","URBANSIZE","URBRUR","USEINTST","USEPUBTR","VEHID","WHODROVE","WHYFROM","WHYTO","WHYTRP1S","WRKCOUNT","DWELTIME","WHYTRP90","TDTRPNUM","TDWKND","TDAYDATE","TRPMILES","WTTRDFIN","VMT_MILE","PUBTRANS","HOMEOWN","HOMETYPE","HBHUR","HTRESDN","HTHTNRNT","HTPPOPDN","HTEEMPDN","HBRESDN","HBHTNRNT","HBPPOPDN","GASPRICE","VEHTYPE","HH_CBSA","HHC_MSA")

foo <- within(foo, {
    URBRUR <- as.factor(URBRUR)
    HHSTFIPS <- as.factor(HHSTFIPS)
    MSACAT <- as.factor(MSACAT)
    })

```
<!--
